---
title: "Capstone project"
author: "StepUp Analytics"
date: "01/05/2021"
output: word_document
---

####################################### What you will learn and Implement #######################################

# > Understand kmeans clustering.
# > Understand retail Data for applying kmeans clustering.
# > Understand the objective.
# > Maths of kmeans clustering.
# > understand Optimum number of cluster.
# > Using elbow method to determine the optimal number of cluster.
# > model fitting
# > Evaluation

# > Objective

# The client is a leading Fashion retailer in Australia. Company runs a display advertising campaign for this brand, where it shows ads to users leading them to make a purchase on the brands website.The given dataset is the Sales data for all users who made a purchase online in the first half of October '17.

# Based on your analysis, arrive at a statistical segmentation of the brands audience based 
# on Revenue. The number of segments is up to you. Please provide definitions of each groups

# > desired Library installation

```{r}
 install.packages("factoextra")
 install.packages("rpivotTable")
 install.packages("cluster")
 install.packages("fpc")
 install.packages("factoextra")
 install.packages("rpivotTable")
 install.packages("ggplot2")
install.packages("dplyr")
 install.packages("magrittr")
```


```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
library(cluster)
library(fpc)
library(factoextra)
library(rpivotTable)
```

# > Setting working directory

```{r}
Path="C:/Users/KAUSHALI ROY/Documents/R(3)/Capstone Project - Kmeans Clustering"
setwd(Path)
getwd()
```

# > reading data

```{r}
Fashion = read.csv('Fashion.csv',header = TRUE,stringsAsFactors = FALSE)
View(Fashion)
head(Fashion,20)
```

# > subsetting/manipulating data to fit kmeans clustering

```{r}
names(Fashion)
str(Fashion)
e<-subset(Fashion, select=20)
names(e)
class(e)
class(e$Revenue.AUD.)
glimpse(e)
```

# > fitting basic model taking a random number of cluster say "3"

```{r}
set.seed(100)
basic_model<-kmeans(e,3)
basic_model$tot.withinss
basic_cluster<-basic_model$cluster
head(basic_cluster)
clusterss<-basic_model$withinss
sum(clusterss)
ggplot(data = e) +aes(x=basic_cluster, y=Revenue.AUD.)+
  geom_point() +xlab("cluster")+ylab("revenue")
```

# > calculating optimum number cluster

```{r}
optimcluster <- function(k){
  cluster <- kmeans(D, k)
  return(cluster$tot.withinss)
}

wss <- sapply(1:20, optimcluster)

optimK <- data.frame(k = 1:20, wss)
head(optimK)
```

Interpretation: The method consists of plotting the explained variation as a function of the number of clusters, and picking the elbow of the curve as the number of clusters to use.

### ploting the k value from 1 to 20 against within sum of square (wss)

```{r}
ggplot(data = optimK) + aes(x=k, y= wss) + geom_point() + geom_line()+
  scale_x_continuous(breaks = seq(1,20,by = 1))

OptimunCluster <- 3
```

# > Model fitting using optimum k
```{r}
model<-kmeans(e, OptimunCluster)
cluster<-model$cluster
head(cluster)

model$centers

mapping<-data.frame(Revenue=e, cluster=cluster)
head(cluster)
ggplot(data=mapping) + aes(x=cluster, y=Revenue.AUD.)+
  geom_point()+ xlab("cluster")+ylab("Revenue")


```


```{r}
write.csv("mapping.csv")
plotcluster(e$Revenue.AUD.,cluster)
plotcluster(x=e$Revenue.AUD., model$cluster, xlab = "revenue", ylab = "cluster")
```

